%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Gophr App} % Job title
{BlueOcean Tech/Dofleini Cuba} % Organization
{La Habana, Cuba.} % Location
{Apr. 2017 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {http://www.gogophr.com}
\item {GoGophr is an innovative digital library which is built by searching across the web using major search engines and building your own portal with the best of content on the concerned subject matter.}
\item {Microservice Architecture/ AngularJS/ Java/ Scala/ NodeJS/ Reactive Programing}
\end{cvitems}
}

%------------------------------------------------

\cventry
{LEAP App} % Job title
{BlueOcean Tech/Dofleini Cuba} % Organization
{La Habana, Cuba.} % Location
{Jan. 2017 - Apr. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {http://leapbrands-all.leapmediainvestments.com}
\item {LEAP show the result of a survey made in US about Brands and TV Programs.}
\item {AngularJS/ Google Charts/ jsPdf}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Police Management System (PMS)} % Job title
{BlueOcean Tech/Dofleini Cuba} % Organization
{La Habana, Cuba.} % Location
{Oct. 2016 - Jan. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {It’s a custom development for police stations in Tarragona Spain. Specially design to cover the main needs of police daily}
\item {AngularJS/ Java Spring}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Management Statistics Information System (SIGE)} % Job title
{Center of Technologies and Data Management (University of Informatics Science)} % Organization
{La Havana, Cuba} % Location
{2013 - 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Design and implementation of statistical computer systems (SIGE)}
\item {Architect of product SIGE v2}
\item {Leading a group of developers to implement SIGE v2}
\item {PHP/ ExtJs/ Javascript}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Tool to collect the information in news published on the internet web sites} % Job title
{Center of Technologies and Data Management (University of Informatics Science)} % Organization
{La Havana, Cuba} % Location
{Jun. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Proceedings of collect information in internet web sites with crawler process}
\item {Python/ PL/SQL}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}

