%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Positions}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------    

\cventry
{Research Engineer} % Job title
{BlueOcean Tech/Dofleini Cuba} % Organization
{La Havana, Cuba} % Location
{Feb. 2016 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {AI Engineer}
\item {NLP Engineer}
\item {ML Engineer}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Researcher} % Job title
{Centre of Computational Mathematics (University of Informatics Science)} % Organization
{La Havana, Cuba} % Location
{Sep. 2014 - Feb. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Research/implementation about Parallel Evolutionary Algorithms}
\item {Implementation of numeric algorithms using Scala/MLlib (Spark)}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Question/answering system consultor (Research Engineer)} % Job title
{Casabe} % Organization
{La Havana, Cuba} % Location
{Jun. 2015 - Oct. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {State of the art analysis about Question/Answering systems}
\item {Organization of the development team}
\item {Development of POCs using: NLTK, OpenNLP, scikit-learn, SparkML, and Clojure}
\item {Definition of quality metrics}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Centre of Internet Studies (University of Informatics Science)} % Organization
{La Havana, Cuba} % Location
{Sep. 2004 - Jun. 2009} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {WebSearcher implementation using Lucene}
\item {Implementation of text representation algorithms}
\item {Web Crawler implementation}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Internship} % Job title
{Centre of Applied-Linguistic} % Organization
{Santiago de Cuba, Cuba} % Location
{Sep. 2000 - Jul. 2002} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Morphologic Analisis design and implementation}
\item {Implementation of a Lemmatization algorithm}
%\item {}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}

